\documentclass{cookbook}
\begin{document}
\tableofcontents
\section{TBD}
\recipe{Belgian Beef Stew}

\begin{ingredients}
    \item 2 lb. beef chuck, cut into 2 in. x \sfrac{1}{2} in. slices
    \item \sfrac{1}{4} cup flour
    \item 4 tbsp. unsalted butter
    \item 4 slices bacon, finely chopped
    \item 6 cloves garlic, finely chopped
    \item 3 medium yellow onions, diced
    \item 2 cups Belgian-style ale
    \item 1 cup beef stock
    \item 2 tbsp. dark brown sugar
    \item 2 tbsp. apple cider vinegar
    \item 3 sprigs thyme
    \item 3 sprigs parsley
    \item 2 sprigs tarragon
    \item 1 bay leaf
\end{ingredients}

Season beef with salt and pepper in a bowl. Heat 2 tbsp. butter in a 6 qt. Dutch oven over medium-high heat. Working in batches, add beef. Cook, turning, until browned, about 8 minutes. Transfer to a plate and set aside.

Add bacon and cook until its fat renders, about 8 minutes. Add remaining butter, garlic, and onions. Cook until caramelized, about 30 minutes.

Add half the beer. Cook, scraping bottom of pot, until slightly reduced, about 4 minutes. Return beef to pot with remaining beer, stock, sugar, vinegar, herbs, flour, and salt and pepper. Boil. Reduce heat to medium-low. Cook, covered, until beef is tender, about 1 \sfrac{1}{2} hours.

\recipe{Chicken Enchilada Bowl}

\begin{ingredients}
    \item 1 lb. boneless skinless chicken thighs
    \item \sfrac{3}{4} cup red enchilada sauce
    \item \sfrac{1}{4} cup water
    \item \sfrac{1}{4} cup chopped onion
    \item 4 oz. can diced green chiles
    \item 1 whole avocado, diced
    \item 1 cup shredded cheese
    \item \sfrac{1}{2} cup sour cream
\end{ingredients}

Turn Instant Pot to saute. Once the pot is hot, add olive oil and sear chicken thighs until lightly brown.

Pour in enchilada sauce and water then add onion and green chiles. Secure Instant Pot lid.

Cook on High Pressure setting for 15 minutes.

Careully remove the chicken and place onto a work surface. Chop or shred chicken then add it back into the Instant Pot.

Pressure cook for additional 5 minutes to allow chicken to absorb flavor and the sauce to reduce.

To Serve, top with avocado, cheese, and sour cream.

\recipe{Instant Pot Beef Stroganoff}

\begin{ingredients}
    \item 1 lb. ground beef
    \item 1 small onion, chopped
    \item 1 clove garlic, minced
    \item 8 oz. white button mushrooms, sliced
    \item 1 tbsp. all-purpose flour
    \item 1 can cream of mushroom soup
    \item 2 \sfrac{1}{4} cups beef broth
    \item 8 oz. wide egg noodle
    \item \sfrac{1}{3} cup sour cream
    \item 2 tbsp. fresh parsley, chopped
\end{ingredients}

Turn Instant Pot to saute. Once the pot is hot, add olive oil and ground beef. Brown the meat, breaking it into small pieces as it cooks, and season it with salt and pepper.

Add onion, garlic and mushrooms and saute for 2 minutes.

Add flour, cream of mushroom soup, beef broth, and noodles and stir to combine.

Secure Instant Pot lid, and turn valve to sealed position. Cook on High Pressure setting for 10 minutes.

When pressure cooking is complete, use a quick release.

Carefully remove the lid and stir mixture. Stir in sour cream, parsley, additional salt and pepper to taste.

\recipe{Avocado Toast}

\begin{ingredients}
    \item 2 large eggs
    \item 2 slices of bread
    \item 1 large avocado
    \item Everything spice seasoning
    \item Pinch of salt, to taste
\end{ingredients}

First poach the eggs. Using a sous vide, bring 4-inches of water to 167\degree F / 75\degree C. Using a slotted spoon, gently lower the eggs into prepared water bath and cook for 12 minutes.

Meanwhile, fill a large bowl halfway with ice and water. Using the slotted spoon, transfer the eggs to ice bath and let sit until cool enough to handle, about 1 minute.

Toast the bread until browned, butting both sides.

Mash the avocado and spread it on the toast. Top the avocado toast with poached eggs. Then sprinkle everything seasoning on top. Add as much or as little of the seasoning as you like and a pinch of salt to taste.

Serve this everything spice poached egg avocado toast warm.

\recipe{Mashed Potatoes}

\begin{ingredients}
    \item 2 lbs. Yukon Gold potatoes, peeled and cut in 2 in. pieces
    \item \sfrac{3}{4} cup whole milk
    \item 2 bay leaves
    \item \sfrac{1}{2} cup unsalted butter
\end{ingredients}

Place potatoes in a large pot and pour in cold water to cover by 1 in. Add salt and bring to a boil. Reduce heat and simmer until potatoes are very tender but not saturated or crumbly, about 20 minutes.

Drain potatoes and return to pot and set over low heat. Gently stir until dry, about 1 minute.

Meanwhile, heat milk, bay leaves, and \sfrac{1}{2} cup butter in a small saucepan over medium heat until butter is melted. Remove from heat.

Pass hot potatoes through a ricer into a large bowl (if allowed to cool, the potatoes will become gummy).

Remove bay leaves from warm milk mixture; discard. Gradually add milk mixture to potatoes, stirring vigorously with a wooden spoon until combined and smooth; season with salt and pepper.

\recipe{Instant Pot Parmesan Risotto}

\begin{ingredients}
    \item 4 tbsp. butter
    \item 1 small onion, finely diced
    \item 2 cloves garlic, minced
    \item 1 \sfrac{1}{2} cups Arborio rice
    \item 4 cups vegetable broth
    \item 3 tbsp. grated parmesan cheese
    \item \sfrac{1}{2} tsp. salt
    \item \sfrac{1}{4} tsp. ground black pepper
    \item \sfrac{1}{2} cup chopped fresh parsley   
\end{ingredients}

Press the Saute button on Instant Pot. Add and melt the butter. Add the onion and stir fry for 3-5 minutes until onions are translucent. Add garlic and rice and cook for an additional minute. Add 1 cup broth and stir for 2-3 minutes until it is absorbed by the rice.

Add remaining 3 cups broth, Parmesan cheese, salt, and pepper. Lock lid.

Press the Manual button and adjust time to 10 minutes. When timer beeps, let pressure release naturally for 10 minutes. Quick release any additional pressure until float valve drops and then unlock lid.

Ladle into bowls and garnish each with \sfrac{1}{8} cup fresh parsley.

\end{document}
